State of the Art in Scientific Workflow Systems

### 2014-05-30 paper.tex
galaxy desc

\paragraph{The P-GRADE Portal/--} The P-GRADE Portal~\cite{pgrade2011}
developed at the MTA SZTAKI Computation and Automation Institute, Budapest,
provides an access to grid computational and storage resources from a web
browser through a specialized workflow oriented grid portal. A workflow
development environment interfaces the users through this web based portal. The
portal interfaces the multiple grid computing middleware and storage resources
as a backend component of the environment. A highlight of P-GRADE portal is
that it provides access to multiple grids and scientific communities in a
single environment leading to a highly collaborative inter-community,
inter-grid research environment. An older version of P-GRADE used the
condor-Dagman as workflow engine while the recent version uses its own in-house
developed workflow engine called Xen. \km{Investigate cloud and GPU capabilities}

%

\paragraph{Galaxy Portal/JSON} Galaxy~\cite{blankenberg-vonkuster-etal:2010} is a
bioinformatics domain SWE based framework developed at the Penn State
University, Pennsilvania. It provides a webportal based environment to build
complex pipelines from an available repository of tools
(\textit{http://g2.bx.psu.edu}). Users can extend the tool repository provided
by Galaxy using their own Galaxy server. One of the major use of Galaxy is to
achieve a mix and match of data analysis tools in order to analyze a vast
repository of genome based database.

>>>>

\paragraph{The P-GRADE Portal/--} The P-GRADE Portal~\cite{pgrade2011}
developed at the MTA SZTAKI Computation and Automation Institute, Budapest,
provides an access to grid computational and storage resources from a web
browser through a specialized workflow oriented grid portal. A workflow
development environment interfaces the users through this web based portal. The
portal interfaces the multiple grid computing middleware and storage resources
as a backend component of the environment. A highlight of P-GRADE portal is
that it provides access to multiple grids and scientific communities in a
single environment leading to a highly collaborative inter-community,
inter-grid research environment. An older version of P-GRADE used the
condor-Dagman as workflow engine while the recent version uses its own in-house
developed workflow engine called Xen. \km{Investigate cloud and GPU capabilities} 
%

\paragraph{Galaxy Portal/JSON} Galaxy~\cite{blankenberg-vonkuster-etal:2010} is a
SWE developed at the Penn State University, Pennsilvania. It provides a
webportal based environment to build complex pipelines from an available
repository of tools (\textit{http://g2.bx.psu.edu}).  Galaxy is currently used
mainly by bioinformatics community. Users can extend the tool repository
provided by Galaxy using their own Galaxy server. One of the major use of
Galaxy is to achieve a mix and match of data analysis tools in order to analyze
a vast repository of genome based database. Galaxy offers a web-based,
interactive platform for data analysis via reusable and reproducible workflows.
While excelling in the usability aspects, the Galaxy environment has a limited
parallelism capabilities and a small number of existing implementations for
interfacing with diverse, scalable computing infrastructures. The user can draw
workflows in which multiple copies of a task are created to operate on multiple
inputs at once, but this is not a scalable approach.
